Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
fixed some typos

\texttt{sample} and \texttt{observe} may appear anywhere in the
code of an Anglican program. To support these forms, the
inference engine must be able to intervene into execution of the
program, perform computations related to inference, and control
further execution of the program. This tight and complicated
interaction between the program and the inference engine
necessiates implementing Anglican as a language rather than a
library.

@@

    \caption{Anglican vs. WebPPL. Running times, in seconds, of
    Anglican and WebPPL, for $100\,000$ iterations of Markov Chain
    Monte Carlo (Lighweight Metropolis-Hastings), averaged over
    100 runs. Anglican outperforms WebPPL on all models.}
    \label{tbl:webppl}
\end{table}
The source code of the examples is available in the
\href{https://bitbucket.org/probprogs/anglican-white-paper}{paper
repository}.

>>>>

\texttt{sample} and \texttt{observe} may appear anywhere in the
code of an Anglican program. To support these forms, the
inference engine must be able to intervene into execution of the
program, perform computations related to inference, and control
further execution of the program. This tight and complicated
interaction between the program and the inference engine
necessitates implementing Anglican as a language rather than a
library.

@@

    \caption{Anglican vs. WebPPL. Running times, in seconds, of
    Anglican and WebPPL, for $100\,000$ iterations of Markov Chain
    Monte Carlo (Lightweight Metropolis-Hastings), averaged over
    100 runs. Anglican outperforms WebPPL on all models.}
    \label{tbl:webppl}
\end{table}
The source code of the examples is available in the
\href{https://bitbucket.org/probprogs/anglican-white-paper}{paper
repository}.
